Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-28 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

If a QIVPM~$\bar{\mu}$ is 0-deterministic, then for a family of
$M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
they can be diagonalized by a common orthonormal basis~$\Omega$.
By restricting to the subspace of commuting events generated by the
set of projectors associated with $\Omega$, the quantum expectation
values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
are equal to the Choquet integral of the corresponding random variables
relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
to $\bar{\mu}$~\citep{HOSTunpublished}. The Choquet integral relative
to 0-deterministic $\bar{\mu}'$ is a singleton set which have an
intuitive the product rule $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
Because the product of the Choquet integrals of individual random
variables relative to $\bar{\mu}'$ is the Choquet integral of the
product of the family relative to $\bar{\mu}'$, we can then prove
that the expectation values of the observables has the corresponding
property: 
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}

>>>>

If a QIVPM\nb$\bar{\mu}$ is 0-deterministic, a family of $M$ commuting
observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ can be
diagonalized by a common orthonormal basis~$\Omega$. By restricting
to the subspace of commuting events generated by the set of projectors
associated with $\Omega$, $\bar{\mu}$ become a 0-deterministic classical
IVPM\nb$\bar{\mu}'$. Moreover, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and the product observables\nb$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
are equal to the Choquet integral of the corresponding random variables
relative to $\bar{\mu}'$\nb\citep{HOSTunpublished}. The Choquet
integral relative to $\bar{\mu}'$ is a singleton set which have an
intuitive the product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
Because the product of the Choquet integrals of individual random
variables relative to $\bar{\mu}'$ is the Choquet integral of the
product of the family relative to $\bar{\mu}'$, the expectation values
of the observables has the corresponding property: 
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
